Karpov, Kasparov, Anand

### 2022-06-23 inst/kka.Rmd

We can now introduce draws but first a change of notation.  The
previous likelihood function can be represented thus:

@@

>>>>

We can now introduce draws but first a change of notation.
Considering repeated trials between entities $1,2,\ldots, r$ with
Bradley-Terry strengths $p_1,\ldots, p_r$ and counts $n_1,\ldots, n_r$ a
suitable likelihood function would be

$$
\left(\frac{p_1}{\sum p_i}\right)^{n_1}\cdot
\left(\frac{p_2}{\sum p_i}\right)^{n_2}\ldots
\left(\frac{p_r}{\sum p_i}\right)^{n_r}
$$

but we may represent this in the following compact form:

$$
\left(\frac{p_1,p_2,\ldots, p_r}{\sum p_i}\right)^{\left(n_1,\ldots n_r\right)}
$$

Or, noting that the sum of the numerators is equal to the common
denominator, even more compactly as $\left(p_1,p_2,\ldots, p_r\right)^{\left(n_1,\ldots n_r\right)}$.

The previous likelihood function can be represented thus:

@@

Package idiom for this would require the following form:

$$
\left(\frac{\lambda p_1, D_1p_1+D_2p_2,p_2}{(\lambda+D_1)p_1+(1+D_2)p_2}\right)^{(a,b,c)}
\left(\frac{p_1, D_1p_1+D_2p_2,\lambda p_2}{(1+D_1)p_1+(\lambda+D_2)p_2}\right)^{(d,e,f)}
$$
